Data-processing

### 2024-05-15 README.Rmd
README includes link to pdf version of report
Antonio's initial edits before submission

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

@@

```{r cover, echo=FALSE}
#| label: cover
knitr::include_graphics("just-transportation_1.png")
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rticles)
```

@@

![The pdf version of this report is available [here](https://github.com/soukhova/Transportation-lit-review/blob/main/just-transportation/just-transportation.pdf)](just-transportation_1.png)
